Gaia's constraints on the $\sim$$150\,M_\odot$ runaway star candidate VFTS682

### 2018-06-08 VFTS682_APJL.tex
minor, likely needs merger

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$,
  R.~P.~van~der~Marel$^{3,4}$, I.~Platais$^{4}$, J. Bestenlehner$^{5}$,
  V.~H\'enault-Brunet$^{6}$,  S.~Justham$^{7,8}$,  A.~de~Koter$^{1}$,
  N.~Langer$^{9}$, H.~Sana$^{10}$, F.~R.~Schneider$^{11}$, J.~S.~Vink$^{12}$}
\affil{$^{1}${Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands} \\
  $^{2}$ {ESA, European Space Astronomy Centre, Apdo. de Correos 78,
    E-28691 Villanueva de la Ca\~nada, Madrid, Spain} \\
  $^{3}$ {Space Telescope Science Institute, 3700 San Martin Drive,
    Baltimore, MD 21218, USA}\\
  $^{4}$ {Center for Astrophysical Sciences, Department of Physics \& Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}\\
  $^{5}${Department of Physics and Astronomy, Hicks Building,
    Hounsfield Road, University of Sheffield, Sheffield S3 7RH, UK}\\
  $^{6}$ {National Research Council, Herzberg Astronomy \&
    Astrophysics, 5071 West Saanich Road, Victoria, BC, V9E 2E7,
    Canada}\\
  $^{7}$ {School of Astronomy \& Space Science, University of the Chinese
    Academy of Sciences, Beijing 100012, China}\\
  $^{8}$ {National Astronomical Observatories, Chinese Academy of
    Sciences, Beijing 100012, China}\\
  $^{9}$ {Argelander-Instit\"ut f\"ur Astronomie, Universit\"at Bonn,
    Auf dem H\"ugel 71, 53121, Bonn, Germany}\\
  $^{10}$ {Institute of Astronomy, KU Leuven, Celestijnenlaan 200 D, B-3001 Leuven, Belgium}\\
  $^{11}$ {Department of Physics, University of Oxford, Keble Road,
    Oxford OX1 3RH, UK} \\
  $^{12}$ {Armagh Observatory, College Hill, Armagh BT61 9DG, UK}\\
}

@@

\begin{table}
  \begin{center}
    \caption{Astrometric parameters for VFTS682. }
    \begin{tabular}{l|c|c}
      \hline
      \hline
      Parameter & Value & Source\\
      \hline
      RA \hfill[degree] &  \phantom{-}84.73 % $\pm$  0.03
                        & \multirow{2}{*}{\cite{evans:11}}\\[5pt]
      DEC \hfill [degree] & -69.07 % $\pm$  0.05
                        & \\[5pt]
      \hline
      $\delta\mu_\mathrm{RA}^{Gaia}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.10$\pm$0.07 & \multirow{2}{*}{\emph{Gaia} DR2}\\[5pt]
      $\delta\mu_\mathrm{DEC}^{Gaia}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.08$\pm$0.09 & \\[5pt]
      \hline
      $\delta\mu_\mathrm{RA}^{HST}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.01$\pm$0.13 & \multirow{2}{*}{\cite{platais:18}}\\[5pt]
      $\delta\mu_\mathrm{DEC}^{HST}$  \hfill[$\mathrm{mas\ yr^{-1}}$] &
                                                                        0.2$\pm$0.1 &
      \\[5pt]
      \hline
      $\delta v_\mathrm{rad}$  \hfill[$\kms$] & 30$\pm$20 & \cite{bestenlehner:11}\\
      \hline
    \end{tabular}
    % \tablecomments
    {The error on the RA and DEC positions, are of order
      $\sim$$10^{-2}\,\mathrm{mas\ yr^{-1}}$ in \emph{Gaia}
      DR2. %REPETITION: %  We adopt the peculiar
      % radial velocity calculated using the  NV $\lambda4944$ line, which is
      % less sensitive to the wind velocity structure (see also \Secref{data:vfts683}).
    }
  \end{center}
  \label{tab:vfts682}
\end{table}

@@

\bibitem[\protect\citeauthoryear{{Hogg}}{{Hogg}}{2018}]{hogg:18}
{Hogg} D.~W.,  2018, ArXiv:1804.07766, \href
  {http://adsabs.harvard.edu/abs/2018arXiv180407766H} {}

@@

\bibitem[\protect\citeauthoryear{{Maeder} \& {Meynet}}{{Maeder} \&
  {Meynet}}{2000}]{maeder:00}
{Maeder} A.,  {Meynet} G.,  2000, \aap, \href
  {http://adsabs.harvard.edu/abs/2000A\%26A...361..159M} {361, 159}

@@

\bibitem[\protect\citeauthoryear{{Ram{\'{\i}}rez-Agudelo}
  et~al.,}{{Ram{\'{\i}}rez-Agudelo} et~al.}{2015}]{ramirez-agudelo:15}
{Ram{\'{\i}}rez-Agudelo} O.~H.,  et~al., 2015, \mn@doi [\aap]
  {10.1051/0004-6361/201425424}, \href
  {http://adsabs.harvard.edu/abs/2015A\%26A...580A..92R} {580, A92}

@@

\bibitem[\protect\citeauthoryear{{Robitaille} \& {Bressert}}{{Robitaille} \&
  {Bressert}}{2012}]{robitaille:12}
{Robitaille} T.,  {Bressert} E.,  2012, {APLpy: Astronomical Plotting Library
  in Python}, Astrophysics Source Code Library (\mn@eprint {ascl} {1208.017})

@@

\bibitem[\protect\citeauthoryear{{de Mink}, {Cantiello}, {Langer}, {Pols},
  {Brott}  \& {Yoon}}{{de Mink} et~al.}{2009}]{demink:09}
{de Mink} S.~E.,  {Cantiello} M.,  {Langer} N.,  {Pols} O.~R.,  {Brott} I.,
  {Yoon} S.-C.,  2009, \mn@doi [\aap] {10.1051/0004-6361/200811439}, \href
  {http://adsabs.harvard.edu/abs/2009A\%26A...497..243D} {497, 243}

>>>>

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$,
  R.~P.~van~der~Marel$^{3,4}$, I.~Platais$^{4}$, J. Bestenlehner$^{5}$,
  V.~H\'enault-Brunet$^{6}$,  S.~Justham$^{1,7,8}$,  A.~de~Koter$^{1}$,
  N.~Langer$^{9}$, H.~Sana$^{10}$, F.~R.~Schneider$^{11}$, J.~S.~Vink$^{12}$}
\affil{$^{1}${Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands} \\
  $^{2}$ {ESA, European Space Astronomy Centre, Apdo. de Correos 78,
    E-28691 Villanueva de la Ca\~nada, Madrid, Spain} \\
  $^{3}$ {Space Telescope Science Institute, 3700 San Martin Drive,
    Baltimore, MD 21218, USA}\\
  $^{4}$ {Center for Astrophysical Sciences, Department of Physics \& Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}\\
  $^{5}${Department of Physics and Astronomy, Hicks Building,
    Hounsfield Road, University of Sheffield, Sheffield S3 7RH, UK}\\
  $^{6}$ {National Research Council, Herzberg Astronomy \&
    Astrophysics, 5071 West Saanich Road, Victoria, BC, V9E 2E7,
    Canada}\\
  $^{7}$ {School of Astronomy \& Space Science, University of the Chinese
    Academy of Sciences, Beijing 100012, China}\\
  $^{8}$ {National Astronomical Observatories, Chinese Academy of
    Sciences, Beijing 100012, China}\\
  $^{9}$ {Argelander-Instit\"ut f\"ur Astronomie, Universit\"at Bonn,
    Auf dem H\"ugel 71, 53121, Bonn, Germany}\\
  $^{10}$ {Institute of Astronomy, KU Leuven, Celestijnenlaan 200 D, B-3001 Leuven, Belgium}\\
  $^{11}$ {Department of Physics, University of Oxford, Keble Road,
    Oxford OX1 3RH, UK} \\
  $^{12}$ {Armagh Observatory, College Hill, Armagh BT61 9DG, UK}\\
}

@@

\begin{table}
  \begin{center}
    \caption{Astrometric parameters for VFTS682. }
    \begin{tabular}{l|c|c}
      \hline
      \hline
      Parameter & Value & Source\\
      \hline
      RA \hfill[degree] &  \phantom{-}84.73 % $\pm$  0.03
                        & \multirow{2}{*}{\cite{evans:11}}\\[5pt]
      DEC \hfill [degree] & -69.07 % $\pm$  0.05
                        & \\[5pt]
      \hline
      $\delta\mu_\mathrm{RA}^{Gaia}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.10$\pm$0.07 & \multirow{2}{*}{\emph{Gaia} DR2}\\[5pt]
      $\delta\mu_\mathrm{DEC}^{Gaia}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.08$\pm$0.09 & \\[5pt]
      \hline
      $\delta\mu_\mathrm{RA}^{HST}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.01$\pm$0.13 & \multirow{2}{*}{\cite{platais:18}}\\[5pt]
      $\delta\mu_\mathrm{DEC}^{HST}$  \hfill[$\mathrm{mas\ yr^{-1}}$] &
                                                                        0.2$\pm$0.1 &
      \\[5pt]
      \hline
      $\delta v_\mathrm{rad}$  \hfill[$\kms$] & 30$\pm$20 & \cite{bestenlehner:11}\\
      \hline
    \end{tabular}
    \tablecomments
    {The error on the RA and DEC positions, are of order
      $\sim$$10^{-2}\,\mathrm{mas\ yr^{-1}}$ in \emph{Gaia}
      DR2. %REPETITION: %  We adopt the peculiar
      % radial velocity calculated using the  NV $\lambda4944$ line, which is
      % less sensitive to the wind velocity structure (see also \Secref{data:vfts683}).
    }
  \end{center}
  \label{tab:vfts682}
\end{table}

@@

% \bibitem[\protect\citeauthoryear{{Hogg}}{{Hogg}}{2018}]{hogg:18}
% {Hogg} D.~W.,  2018, ArXiv:1804.07766, \href
%   {http://adsabs.harvard.edu/abs/2018arXiv180407766H} {}

@@

% \bibitem[\protect\citeauthoryear{{Maeder} \& {Meynet}}{{Maeder} \&
%   {Meynet}}{2000}]{maeder:00}
% {Maeder} A.,  {Meynet} G.,  2000, \aap, \href
%   {http://adsabs.harvard.edu/abs/2000A\%26A...361..159M} {361, 159}

@@

% \bibitem[\protect\citeauthoryear{{Ram{\'{\i}}rez-Agudelo}
%   et~al.,}{{Ram{\'{\i}}rez-Agudelo} et~al.}{2015}]{ramirez-agudelo:15}
% {Ram{\'{\i}}rez-Agudelo} O.~H.,  et~al., 2015, \mn@doi [\aap]
%   {10.1051/0004-6361/201425424}, \href
%   {http://adsabs.harvard.edu/abs/2015A\%26A...580A..92R} {580, A92}

@@

% \bibitem[\protect\citeauthoryear{{Robitaille} \& {Bressert}}{{Robitaille} \&
%   {Bressert}}{2012}]{robitaille:12}
% {Robitaille} T.,  {Bressert} E.,  2012, {APLpy: Astronomical Plotting Library
%   in Python}, Astrophysics Source Code Library (\mn@eprint {ascl} {1208.017})

@@

% \bibitem[\protect\citeauthoryear{{de Mink}, {Cantiello}, {Langer}, {Pols},
%   {Brott}  \& {Yoon}}{{de Mink} et~al.}{2009}]{demink:09}
% {de Mink} S.~E.,  {Cantiello} M.,  {Langer} N.,  {Pols} O.~R.,  {Brott} I.,
%   {Yoon} S.-C.,  2009, \mn@doi [\aap] {10.1051/0004-6361/200811439}, \href
%   {http://adsabs.harvard.edu/abs/2009A\%26A...497..243D} {497, 243}
